junk_final_assignment

### 2022-11-27 draft_final_assingment.Rmd
Parties are now within the dataset
Wordclouds for congresses and parties

```{r}
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
```

@@

df %>%
  mutate(party = ifelse(str_detect(Sponsor, "[R-"), "Republican", 
                   ifelse(str_detect(Sponsor, "[D-"), "Democrat", NA)))
```

>>>>

```{r}
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
```

@@

df$party <- ifelse(str_detect(df$Sponsor, "R-[A-Z]{2,}"),"Republican", ifelse(str_detect(df$Sponsor,"D-[A-Z]{2,}"),"Democrat", NA))
```

## Creating a corpus
```{r}
df_corp <- df
df_corp <- df_corp %>% rename(text = Summary)
corp <- corpus(df_corp)

````

##Creatung a dfm from the corpus
```{r}
dfm <- corp %>%
  tokens(remove_punct = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  dfm()

````

##Most common words in the corpus
```{r}

dfm %>% colSums() %>% sort(decreasing = TRUE) %>% head(20)
```

#Wordcloud comparing Democrats and Republicans
```{r}
dfmat2 <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$party) %>%
    dfm_trim(min_termfreq = 3)

textplot_wordcloud(dfmat2, comparison = TRUE, max_words = 300,
                   color = c("blue", "red"))

```

#Wordcloud comparing Congress
```{r}
dfmat3 <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Congress) %>%
    dfm_trim(min_termfreq = 3)

textplot_wordcloud(dfmat3, comparison = TRUE, max_words = 300,
                   color = c("blue", "red"))

```
